### 2023-10-24 exploreation.Rmd
minor cleaning

```{r}

N <- 100
ki  <-  3
km  <-  1
K  <- ki+km
ntraits=list(a=c(
etopo <- read.csv(textConnection(
"altitudes,colours
10000,#FBFBFB
4000,#864747
3900,#7E4B11
2000,#9B8411
1900,#BD8D15
300,#F0CF9F
0,#307424
-1,#AFDCF4
-12000,#090B6A
"
), stringsAsFactors=FALSE)
etopo$altitudes01 <- scales::rescale(etopo$altitudes)

@@

z=4
a=rep(0,3)
adaptiveTraits=a
age  <- vector()
community  <- vector()
population  <- cbind(age=age,community=community)

community <- list(
                  coordinates=cbind(x=vector(mode="numeric",length=K),y=vector(mode="numeric",length=K)),
                  traits=cbind(a1=vector(mode="numeric",length=K),a2=vector(mode="numeric",length=K),a3=vector(mode="numeric",length=K)),
                  size=vector(mode="numeric",length=K)

                  )
source("R/population.R")
N=100
z=4 #number of neutral traits
ki <- 5
km <- 2
K  <-  ki+km
m=.2 #proba marriage
b=.1 #HG birth rate
r=.2 #farmer scale param
rho #marriage rule

>>>>

```{r}
etopo <- read.csv(textConnection(
"altitudes,colours
10000,#FBFBFB
4000,#864747
3900,#7E4B11
2000,#9B8411
1900,#BD8D15
300,#F0CF9F
0,#307424
-1,#AFDCF4
-12000,#090B6A
"
), stringsAsFactors=FALSE)
etopo$altitudes01 <- scales::rescale(etopo$altitudes)

@@

source("R/population.R")
N=100
z=4 #number of neutral traits
ki <- 5
km <- 2
K  <-  ki+km
m=.2 #proba marriage
b=.1 #HG birth rate
r=.2 #farmer scale param
rho #marriage rule
